---
title: "Final Project"
author: "Ogy"
date: "2/13/2022"
output: html_document
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Store string containing all required packages
my_packages <- c('pdftools', 'stringr', 'stopwords', 'igraph', 'RColorBrewer', 'dplyr') # create a vector of str objects and put packages needed
```

Determine which packages in list has already been installed

``` {r installed-packages}
# Store all installed packages
ya_installed <- library()$results[,1] # installed

# Check whether required packages are already installed and grab only those that still need installation
need_install<-my_packages[!(my_packages %in% ya_installed)] # not in installed variable

#install required packages
lapply(need_install, install.packages, character.only = TRUE) # install all required packages
```

Now, load only unloaded packages

``` {r unloaded-packages}
# Store all installed packages
ya_loaded <- (.packages())

# Check whether required packages are already installed and grab only those that still need installation
need_load<-my_packages[!(my_packages %in% ya_loaded)]

# Load required packages
lapply(need_load, require, character.only = TRUE)
```

## Scrape Interim Report 

``` {r scrape-text}
# Extract text from pdf
text <- pdf_text("MonteCristo.pdf")
# Convert text to dataframe
text_df <- as.data.frame(text)
```

```{r chapter3}
# Each page of pdf is one row
MonteCristo <- text_df[9:284,]

```


``` {r}
# Convert desired row(s)/page(s) to character string
MonteCristo  <- as.character(MonteCristo)
```

### Removing line breaks

```{r}
# Replace all instances of "\n" (newline) with a space - use escape characters
# You have to add a space otherwise words will run together
MonteCristo <- str_replace_all(MonteCristo, "\\\n", " ")
```


### Delete all punctuation

Because we are going to look at 2 grams, we are going to remove all punctuation.  

``` {r}
#Replace punctuation with no space

# Delete all quotation marks - these are left and right quotation marks
MonteCristo <- str_replace_all(MonteCristo, "“", "")
MonteCristo <- str_replace_all(MonteCristo, "”", "")

# Delete all commas
MonteCristo <- str_replace_all(MonteCristo, ",","")

MonteCristo <- str_replace_all(MonteCristo, ";","")
MonteCristo <- str_replace_all(MonteCristo, ":","")

```

Finally, we clean up redundant spaces

``` {r}
# Replace multiple spaces with one space
# s+ means 1 or more spaces.  \\ are escape characters
MonteCristo <- str_replace_all(MonteCristo, "\\s+", " ")
```


Check to make sure there isn't anything else that needs removing, such as numbers.


### Cleaning for an effective network graph

We now want to make sure that our words will be recognized as the same when we construct relationships, so we have to converting everything to lowercase. Then we will use a for loop to define an edgelist.

```{r}
# Convert all text to lowercase
MonteCristo <- tolower(MonteCristo)
```

``` {r}
# Identify stop words
# stopwords gives us a list of such words
# otherwise we could manually define these, or even add to this list
stopwords_regex = paste(stopwords('en'), collapse = '\\b|\\b')
stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
MonteCristo<- str_replace_all(MonteCristo, stopwords_regex, '')
```

If we were looking at word/sentence relationships, we may have wanted to keep periods and question marks first to define sentences before breaking up into words. 

``` {r}
# saving as MonteCristo for duple
# Delete all question marks (use escape characters)
MonteCristo <- str_replace_all(MonteCristo, "\\?", "")

# Delete all periods
MonteCristo <- str_replace_all(MonteCristo, "\\.", "")

```

``` {r}
# Replace multiple spaces with one space

# s+ means 1 or more spaces.  \\ are escape characters
MonteCristo <-str_replace_all(MonteCristo, "\\s+", " ")
```

```{r}
#removing all parenthesis 
MonteCristo <- str_replace_all(MonteCristo, "\\(", "")
MonteCristo <- str_replace_all(MonteCristo, "\\)", "")

```

```{r}
#remove all numbers
MonteCristo <- gsub('[0-9]+',"", MonteCristo)

```

```{r}
#Remove multiple space with one space
MonteCristo <- str_replace_all(MonteCristo, "\\s+", " ")
```

```{r}
# Delete spaces at the start and end of our text
MonteCristo<-trimws(MonteCristo, "both")
```

```{r}
# Clear again 
MonteCristo <- str_replace_all(MonteCristo, "\\/", "")
#MonteCristo <- str_replace_all(MonteCristo, "\\- ", "-")
MonteCristo <- str_replace_all(MonteCristo, "\\ -","")
MonteCristo <- str_replace_all(MonteCristo, "\\‘","")
MonteCristo <- str_replace_all(MonteCristo, "\\’","")
MonteCristo <- str_replace_all(MonteCristo, "\\--", "-")
MonteCristo <- str_replace_all(MonteCristo, "—", "")
MonteCristo <- str_replace_all(MonteCristo, "!", "")
MonteCristo <- str_replace_all(MonteCristo, "\\*", "")
MonteCristo <- str_replace_all(MonteCristo, " s ", " ")
MonteCristo <- str_replace_all(MonteCristo, " m ", " ")
MonteCristo <- str_replace_all(MonteCristo, " ve ", "")
MonteCristo <- str_replace_all(MonteCristo, " re ", "")
MonteCristo <- str_replace_all(MonteCristo, "é", "e")
MonteCristo <- str_replace_all(MonteCristo, "è", "e")
MonteCristo <- str_replace_all(MonteCristo, "isnt", "")
MonteCristo <- str_replace_all(MonteCristo, "wasnt", "")
```

``` {r}
# Replace multiple spaces with one space
MonteCristo <- str_replace_all(MonteCristo, "\\s+", " ")

MonteCristo<-trimws(MonteCristo, "both")
```
### Get a vector of words
We now have one list of words in a 1x1 matrix. We need to convert that to a vector with one word in each slot.

``` {r}
# Remember that strsplit returns a list of lists
MonteCristo_ls <- str_split(MonteCristo, " ")
```

```{r}
MonteCristo_vec <- unlist(MonteCristo_ls)
```
## Get a vector of words

We now have one list of words in a 1x1 matrix. We need to convert that to a vector with one word in each slot.

```{r}
MonteCristo_vec <- vector()
for (i in 1:length(MonteCristo_ls)) {
  MonteCristo_vec <- append(MonteCristo_vec, MonteCristo_ls[[i]])
}
```

### Convert the vector of consectutive words into an edgelist

``` {r}
# Create an empty dataframe to hold each edgelist row
# It should have 2 columns and 1 row
# A for-loop will overwrite this for each loop
MonteCristo_row <- as.data.frame(matrix(ncol = 2, nrow = 0))

MonteCristo_el <- as.data.frame(matrix(ncol = 2, nrow = 0))
```

## Trigram for loop
``` {r}
# for loop for creating a trigram for interim report

for (i in 1:(length(MonteCristo_vec)-1)) {
  MonteCristo_row <- c(MonteCristo_vec[i], MonteCristo_vec[i+1])
  MonteCristo_el <- rbind( MonteCristo_el, MonteCristo_row)
  if (i == 1000){
    print("hi")}
}
colnames(MonteCristo_el) <- c('word', 'next')
```

``` {r}
# Convert our edge list to the R data type matrix
MonteCristo_el_mat <- as.matrix(MonteCristo_el)
MonteCristo_el_mat <- na.omit(MonteCristo_el_mat)
#Clean all disconnected words and number/NA entries
#MonteCristo_el_mat <- MonteCristo_el_mat[-c(21018,),]

#Clean all disconnected words and number/NA entries
MonteCristo_el_mat <- na.omit(MonteCristo_el_mat)
MonteCristo_list1 <- list("edmond", "dantes", "abbe", "faria", "fernand", "prison", "guard", "cell", "jailer", "island")
MonteCristo_list2 <- list("monte", "cristo", "count", "franz", "albert", "island", "visit", "italy")
MonteCristo_list3 <- list("house", "love", "paris", "mansion", "posion", "die", "servant")
```


## A summary of our graph objects

``` {r}
# Create a network graph object
MonteCristo.g <- graph_from_edgelist(MonteCristo_el_mat, directed = T)
# use summary to check it out

#used for ploting k-core. Chlnge the number 5 in the for loop with the respective number of coreness you wish to plot
for (i in 5 :0){
Edge = which(degree(MonteCristo.g)==i)
MonteCristo.g = delete.vertices(MonteCristo.g, Edge)
}

#Summary statistics of the graph object
E(MonteCristo.g)
V(MonteCristo.g)
summary(MonteCristo.g)

```


## Define shapes and colors for the key words

``` {r}
# Define the color of the different key words
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_el_mat[,1]]$color <- "#91bfdb"  
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_list1]$color <- "#fc8d59"
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_list2]$color <- "#de2d26"
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_list3]$color <- "#a1d99b"

# Define the shape of the different words
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_el_mat[,1]]$shape <- "circle"
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_list1]$shape <- "square"
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_list2]$shape <- "square"
V(MonteCristo.g)[V(MonteCristo.g)$name %in% MonteCristo_list3]$shape <- "square"
```

## Plotting
``` {r}
png(file="MonteCristokcore5.png", width=8000, height=8000) #save the plot as a png file with width 8000 and height 8000
plot(MonteCristo.g,#plot words_matrix.g
    vertex.size = 1, #make the size of the nodes smaller
    vertex.label.cex = 0.7, #make the size of the node labes smaller
    vertex.label.distance = 0, #set the labels directly on the nodes
    #vertex.color = "#91bfdb", #select a specific rgb color for the nodes
    edge.curved = 0.35, # add a small curviture to the edges
    vertex.label.color = "black", #change the color of the node labels to black
    edge.color = rgb(113/255, 114/255, 113/255, 0.2), #change the edge color to a specific rgb color 
    layout = layout_with_fr
    ) #use Fructerman-Reingold layout for the network
dev.off() 
```

## Ego Networks

Below we present the code for plotting the ego networks. In this example, we plot the netwofrk for the word "dantes", but this code can be modified easily to plot the ego network for any word in the report. Foloow the instructions in the comments to plot for a different word. 

```{r}
#EXAMPLE of how to plot the ego network for the word data
names <- V(MonteCristo.g)$name #assign the names of the words to  name 
#View(names) #uncomment this line to check the corresponding number of the word you would wish to plot a network for -- type the word in the search box once you view the file names
o <- induced_subgraph(MonteCristo.g, c(29, neighbors(MonteCristo.g,29))) #put the number from the previous part in the induced_subgraph and the neighbors command in this line
degree <- log(degree(o, mode = "all"))/3 #assign the degree of the words in the network to the object degree for use later in plotting #remove log if nodes too small
b <- "dantes" #put the word you are making the ego network for instead of "data"

#Change the colors for the words in the network
V(o)[V(o)$name %in% c(b)]$color <- "#fc8d59" #use this color for the word in b
V(o)[!(V(o)$name %in% c(b))]$color <- "#91bfdb" #use this color for all other words

#Change the shapes for ch3
V(o)[V(o)$name %in% c(b)]$shape <- "square" #set the shape of the the desired word to square
V(o)[!(V(o)$name %in% c(b))]$shape <- "circle" #set the shape of the rest of the nodes to circle

###PLOTTING
png(file=b, width=3000, height=3000, res = 100) #save the plot as a png file wit hwidth 6000 and height 6000
plot(o,#plot the ego network for data
    vertex.size = degree, #make the size of the nodes smaller
    vertex.label.cex = .7, #make the size of the node labes smaller
    vertex.label.distance = 0, #set the labels directly on the nodes
    #vertex.color = "#91bfdb", #select a specific rgb color for the nodes
    edge.curved = 0.35, # add a small curviture to the edges
    vertex.label.color = "black", #change the color of the node labels to black
    edge.color = rgb(113/255, 114/255, 113/255, 0.2), #change the edge color to a specific rgb color 
    layout = layout_with_fr #use Fructerman-Reingold layout for the network
    )
dev.off() 
```

You can follow similar procedure to create all the ego networks for the interim report as well by changing the graph object in the first and second commands (names <- V(MonteCristo.g)$name and o <- induced_subgraph(MonteCristo.g, c(1, neighbors(MonteCristo.g,1)))) in this chunk to the graph object for the interim report.


## Centrality Analysis
```{r}

#degree centrality 
cent.degree <- degree(MonteCristo.g)
    ind <- order(-cent.degree)
    cent.degree[ind][1:50]
#Betweeness centrality
cent.bt <- betweenness(MonteCristo.g)
    ind1 <- order(-cent.bt)
    cent.bt[ind1][1:50]
#Closeness centrality
cent.close <- closeness(MonteCristo.g)
    ind2 <- order(-cent.close)
    cent.close[ind2][1:50]
#Eigenvector centrality
cent.eig <- evcent(MonteCristo.g)
    names(cent.eig$vector) <- V(MonteCristo.g)$name
    ind3 <- order(-cent.eig$vector)
    cent.eig$vector[ind3][1:50]
```
